The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
integrate edits intro

## Introduction
Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al. 2015). Animals and landscapes are influenced across scales processes as global as climate and productivity (Field et al. 2009), and species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013). The effect of scale in ecology has been explored through species distribution modelling (Elith et al. 2009), habitat selection (Mayor et al. 2007), and food webs (Sugihara et al. 1989). Scale can be considered throughout ecology, including animal behaviour and the social environment that animals experience.

Sociality exists across scales (Whitehead 2008). For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group [@Franks2010]. Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges. In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (see Glossary; Farine et al. 2015).

Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al. 2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides insight into the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use and innovation of traditional social network analysis (Webber & Vander Wal 2019), it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al. 2019).

Unlike traditional *monolayer* social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and neural networks (Silk et al. 2018). The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.

Here, we discuss and integrate variation in social, spatial, and temporal scales within a multilayer network framework (Figure 1). We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a fission-fusion social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al. 2019). We use this case study to address two principal questions associated with scale-dependent multilayer networks. First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems? Second, can variation in social, spatial, and temporal scale improve predictions associated with seasonal differences in resource availability and social association? We conclude with perspectives for future development and application of scale in multilayer networks with respect to habitat selection and space use (Van Moorter et al. 2016), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al. 2019).

>>>>

## Introduction
Our inference regarding the ecological processes underlying ecological patterns are directly linked to the scale at which they are observed (Levin 1992; Allen et al. 2015). Animals are influenced across scales, through processes such as species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013) and global climate and productivity (Field et al. 2009). Multiscale ecology has been integrated into species distribution modelling (Elith et al. 2009), habitat selection (Mayor et al. 2007), and food webs (Sugihara et al. 1989). Meanwhile, in the context of animal behaviour, certain behaviours are scale dependent, for example, acoustic communication in birds occurs over variable spatial scales (Luther 2009). We posit that animal behaviour and, more specifically, the social environment that animals experience must also be scale-dependent.
Sociality exists across both temporal and spatial scales (Whitehead 2008). For example, grooming requires close spatial proximity between conspecifics and occurs over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group (Figure 1, Franks et al. 2010). Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges. In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over coarser spatial and temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Thus, we define social scale as the type of social relationship observed that can be explicitly defined and measured (Farine et al. 2015). 
Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al. 2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides insight into the structure of social communities and social network properties, which can influence population dynamics and evolutionary processes (Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use and innovation of traditional social network analysis (Webber & Vander Wal 2019), it typically considers a single scale of sociality in a given network (monolayer), drastically simplifying the potential complexity of animal social systems (Finn et al. 2019).
Unlike traditional monolayer social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and neural networks (Silk et al. 2018). The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
Our study is motivated by behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al. 2019). We use this case study to address two principal questions associated with scale-dependent multilayer networks. First, to what degree does the social scale of relationships, spatial scale of landscapes, and temporal scale of analysis influence our ability to interpret complex social systems? Second, can variation in social, spatial, and temporal improve predictions associated with biological differences in seasonal resource availability and social association? We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al. 2019).
